Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae.

### 2020-11-08 results.tex
More work. Almost done.

% !TEX root = ccsn.tex
\section{Detection sensitivity with Advanced gravitational wave detectors}
\label{sec:results}

@@

\tf{We probably need a better title for this section.}

@@

We perform the same analysis using the design sensitivity curve of AdV and expected sensitivity curves for the third-generation 
GW detectors. The results for the former are reported in Table \ref{tab:results}. We focus now on third-generation detectors whose results are reported in Table \ref{tab:results} and shown in Fig.~\ref{fig:s20--SFHo_all3G}. In Europe the Einstein Telescope project proposes to host in a 10-km equilateral triangle configuration three low-power low-frequency cryogenic interferometers as well as three high-power high-frequency interferometers. Three sensitivity curves, ET-B, ET-C and ET-D corresponding to different options and stages of the project~\cite{Hild_2011} are considered in our study (cf.~Fig.~\ref{fig:spectrum}). The US based project Cosmic Explorer~\cite{reitze2019cosmic} is expecting to reach its design
sensitivity circa 2040 through two phases labeled CE1 and CE2, whose sensitivity curves are also shown in Figure~\ref{fig:spectrum}.

%%%

@@

Figure \ref{fig:s20--SFHo_all3G} shows $\Delta$ as function of the source distance for {\texttt s20S}
waveform for the five third-generation detector configurations we analyze. Overall, the ratio is well reconstructed up to distances
in the range \unit[100--200]{kpc} which represents an improvement of a factor 10 with respect to
Advanced LIGO and Advanced Virgo detectors. We can also note that the Einstein Telescope results lay in
between the 2 Cosmic Explorer results. This is confirmed for all other waveforms, expect {\texttt s25}
for which the maximal distance reach in CE2 is significantly lower than CE1. This is partly due to the
small variation of the reconstruction quality to the distance of the source making the estimation of $d_r$
rather uncertain for this waveform. All results are summarized in Table \ref{tab:results} and Figure
\ref{fig:distances}. It is remarkable that with 3G detectors the ratio could be reconstructed for sources
located up to several hundred of kpc. It is nevertheless important to note the rather wide range obtained
for the different waveforms probing a large range of progenitor masses.
We did not find any correlation between the mass of the progenitor and $d_r$, nor the equation of state.
On the other hand, the quality
of the ratio reconstruction depends on the signal-to-noise ratio, expressed in Table \ref{tab:results} by
$d_{det}$.

>>>>

% !TEX root = ccsn.tex
%\section{Detection sensitivity with Advanced gravitational wave detectors}
\section{Detectability prospects}
\label{sec:results}

@@

@@

We perform the same analysis using the design sensitivity curve of AdV and expected sensitivity curves for third-generation 
GW detectors. The results for the former are reported in Table \ref{tab:results} and are discussed below. We focus now on third-generation detectors, presenting our findings in Table \ref{tab:results} and in Fig.~\ref{fig:s20--SFHo_all3G}. In Europe the Einstein Telescope project proposes to host in a 10-km equilateral triangle configuration three low-power, low-frequency, cryogenic interferometers as well as three high-power, high-frequency interferometers. Three sensitivity curves, ET-B, ET-C and ET-D corresponding to different options and stages of the project~\cite{Hild_2011} are considered in our study (cf.~Fig.~\ref{fig:spectrum}). The US based project Cosmic Explorer~\cite{reitze2019cosmic} is expecting to reach its design
sensitivity circa 2040 through two phases labeled CE1 and CE2. Their corresponding sensitivity curves are also shown in Fig.~\ref{fig:spectrum}.

Figure \ref{fig:s20--SFHo_all3G} displays $\Delta$ as a function of the source distance for the five third-generation detector configurations we analyze. As before, we use the {\texttt s20S} waveform model as a reference case.  This figure shows that,  overall, the ratio is well reconstructed up to distances in the range \unit[100--200]{kpc} which represents an improvement of a factor 10 with respect to Advanced LIGO and Advanced Virgo detectors. We can also note that the Einstein Telescope results lay in between the 2 Cosmic Explorer results. This is confirmed for all other waveforms, expect {\texttt s25}
for which the maximal distance reach in CE2 is significantly lower than CE1. This is partly due to the
small variation of the reconstruction quality to the distance of the source making the estimation of $d_r$
rather uncertain for this waveform. All results are summarized in Table \ref{tab:results} and Figure
\ref{fig:distances}. It is remarkable that with 3G detectors the ratio could be reconstructed for sources
located up to several hundred of kpc. It is nevertheless important to note the rather wide range obtained
for the different waveforms probing a large range of progenitor masses.
We did not find any correlation between the mass of the progenitor and $d_r$, nor the equation of state.
On the other hand, the quality
of the ratio reconstruction depends on the signal-to-noise ratio, expressed in Table \ref{tab:results} by
$d_{det}$.

@@
